\chapter*{Chapter 92: \\
	Fair Housing}
    \addstarredchapter{Chapter 92: Fair Housing}
    \minitoc
    \pagebreak

\section{Declaration of Fair Housing Policy}
Discrimination with regard to housing on the basis of race, sex, creed, religion, marital status, and disability adversely affects the health, welfare, peace, and safety of the community.  Persons subject to the discrimination suffer depressed living conditions, and create conditions which endanger the public peace and order. The public policy of the city is declared to be to foster equal opportunity for all to obtain decent, safe and sanitary housing without regard to their race, creed, color, national origin, marital status, disability status, sex and strictly in accord with their individual merits as human beings. It is also the policy of the city to protect all persons from all unfounded charges of discrimination.\footnote{(‘83 Code, SEC. 10.50, Subd. 1)}
\section{Definitions\footnote{(‘83 Code, SEC. 10.50, Subd. 2)}}
For the purpose of this chapter the following definitions shall apply, unless the context clearly indicates or requires a different meaning.
\begin{description}
    \item[DISABILITY] A mental or physical condition which constitutes a handicap.  Nothing in this section shall be construed to prohibit any program, service, facility or privilege afforded to a person with a disability which is intended to habitate, rehabilitate or accommodate that person.
    \item[DISCRIMINATE or DISCRIMINATION] Includes segregate or separate.
    \item[MARITAL STATUS] The standing, state or condition of one as single or married person.
\end{description}

\section{Prohibited Acts in Regard to Housing\footnote{(‘83 Code, SEC. 10.50, Subd.}}
It is an unlawful discriminatory practice and unlawful:
\begin{enumerate}[{\indent}A)]
    \item For any person to discriminate on grounds of race, creed, religion, color, sex, marital status, status with regard to public assistance, national origin, age or disability, in the sale, lease, or rental of any housing unit or units.
    \item For any broker, salesperson or other person acting in behalf of another to so discriminate in the sale, lease, or rental of any housing unit or units belonging to the other person.
    \item For any person engaged in the business of financing the purchase, rehabilitation, remodeling or repair of housing units or in the business of selling insurance with respect to housing units to refuse to provide the financing or insurance or to discriminate with regard to the terms or conditions thereof by reason of the race, color, sex, religion, creed, national origin, marital status, status with regard to public assistance, age or disability of the applicant or because of the location of the unit or units in areas of the city occupied by persons of a particular race, color, sex, religion, creed, national origin, marital status, status with regard to public assistance, age or disability; or to discriminate by treating differently any person or group of persons who desire to purchase, lease, acquire, construct, rehabilitate, repair or maintain real property in a specific urban area because of social, economic or environmental conditions of the area in the granting, withholding, extending, modifying or renewing, or in the rates, terms, conditions, or privileges of any such financial assistance or in the extension of services in connection therewith.  The bona fide programs of federal, state or local governmental units or agencies, however structured or authorized to upgrade or improve in any manner a specific urban area shall not be deemed to be a violation of this section.
    \item For any person, having sold, leased, or rented a housing unit or units to any person, to discriminate with respect to facilities, services, or privileges of occupancy by reason of race, color, sex, creed, religion, national origin, age or disability, marital status or status with regard to public assistance.
    \item For any person to make or publish any statement evidencing an intent to discriminate, on grounds of race, creed, religion, color, sex, national origin or ancestry, marital status, status with regard to public assistance, age or disability, in the sale, lease, or rental of a housing unit or units.
    \item For any person to make any inquiry regarding race, color, sex, creed, religion, national origin, marital status, status with regard to public assistance, age or disability, or to keep any record or use any form of application, designed to elicit the information, in connection with the sale, lease, rental, or financing of a housing unit or units.
    \item For any person, for the purpose of inducing a real estate transaction from which he or she may benefit financially:
    \begin{enumerate}[{\indent\indent}1)]
        \item To represent that a change has occurred or will or may occur in the composition of the block, neighborhood, or area in which the property is located, in respect of the race, color, sex, creed, religion, national origin, marital status, status with regard to public assistance, age or disability of those living there; or
        \item To represent that this change will or may result in the lowering of property values, an increase in crime, or anti-social behavior, or a decline in the quality of schools in the block, neighborhood, or area concerned.
    \end{enumerate}
    \item Nothing in this section shall be construed to require any person or group of persons selling, renting or leasing property to modify the property in any way, or exercise a higher degree of care for a person having a disability than for a person who does not have a disability; nor shall this section be construed to relieve any person or persons regardless of any disability in a written lease, rental agreement, or contract or purchase or sale, or to forbid distinctions based on the inability to fulfill the terms and conditions, including financial obligations of the lease, agreement or contract.
    \item The provisions of this section shall not apply to:
    \begin{enumerate}[{\indent\indent}1)]
        \item The rental of a portion of a dwelling containing accommodations for two families, one of which is occupied by the owner; or
        \item The rental by an owner or occupier of a one-family accommodation in which he or she resides of a room or rooms in the accommodation to another person or persons if the discrimination is by sex, marital status, status with regard to public assistance or disability. Nothing in this section shall be construed to require any person or group of persons selling, renting or leasing property to modify the property in any way, or exercise a higher degree of care for a person having a disability than for a person who does not have a disability; nor shall this section be construed to relieve any person or persons of any obligations generally imposed on all persons regardless of any disability in a written lease, rental agreement, or contract of purchase or sale, or to forbid distinctions based on the inability to fulfill the terms and conditions, including financial obligations, of the lease, agreement or contract.
    \end{enumerate}
\end{enumerate}

\section{Enforcement Procedures}
The city is designated as the enforcement agency for this chapter and shall have the power to receive, hear and determine complaints as provided herein. The proper official shall investigate any complaint delivered to the city. The city shall promptly investigate, upon complaint or upon its own motion, any violations of this section.  If after investigation, it shall have reason to believe a violation has occurred it may refer the matter to the City Attorney for criminal prosecution, initiate civil enforcement procedures as herein provided, or enter into a settlement agreement which, when approved by the city shall have the same force as a city order.\footnote{(‘83 Code, SEC. 10.50, Subd. 4)}

\section{Statute of Limitations}
No action may be brought for civil enforcement or criminal prosecution unless the charge of alleged discriminatory practice was filed with the city within 180 days from the occurrence of the practice.\footnote{(‘83 Code, SEC. 10.50, Subd. 5)}

\section{Civil Enforcement Procedure\footnote{(‘83 Code, SEC. 10.50, Subd. 6)  (Ord. 527, effective 12-20-80)}}
Civil enforcement procedures shall be prosecuted by the city before the Council in the following manner:
\begin{enumerate}[{\indent}A)]
    \item The city shall serve upon respondent by certified mail a complaint, signed by it, which shall set forth a clear and concise statement of the facts constituting the violation, set a time and place for hearing, and advise the respondent of his or her right to file an answer to appear in person or by an attorney and to examine and cross-examine witnesses.
    \item The hearing shall not be less than 20 days after service of the complaint.  At any time prior to the hearing the respondent may file an answer.  Facts not denied by answer shall be deemed admitted.  If the answer sets out new matter, it shall be deemed denied by the city.
    \item The complaint or answer may be amended at any given time prior to the hearing with the consent of the opposing party.
    \item Hearings shall be before the Council.
    \item The city may obtain subpoenas from the district court to compel the attendance of witnesses and the production of documents at any hearing.
    \item If, after hearing, the panel shall conclude that a violation has occurred, it shall prepare an order which may contain any provision deemed desirable to do justice to the complainant or to prevent further violations.  It may include provisions which require the respondent to rent, sell, or lease particular housing to the complainant or to do any other thing as may be just.  The panel’s findings of fact and order shall be served on the respondent and each member of the Council by mail shall become the findings and order of the city unless, within ten days after mailing of the findings and order, the city shall revoke or amend the order, but any order of a panel may be modified by the city at any time.
\end{enumerate}
