\chapter*{Chapter 31: \\
	City Officials}
    \addstarredchapter{Chapter 31: City Officials}
    \minitoc
    \pagebreak

\section{City Administrator}
\index{CITY OFFICIALS!City Administrator}
\subsection{}
The City Administrator shall be the chief administrative officer of the City. The City Administrator shall be chosen by the Council solely on the basis of training, experience, executive and administrative qualifications. The City Administrator need not be a resident of the City at the time of the appointment, but may reside outside the City while in office only with approval of the Council. The City Administrator shall be appointed for an indefinite term and may be removed at any time by an affirmative vote of five Council Members or four Council Members and the Mayor or Assistant Mayor in the event of a tie.
\subsection{Powers And Duties Of The City Administrator.}
\subsubsection*{Subdivision 1.}
The City Administrator shall be responsible to the Council for the administration of the City’s affairs. The City Administrator shall have the powers and duties set forth in the following subdivisions:
\subsubsection*{Subdivision 2.}
The City Administrator shall see that this Charter and the laws, ordinances and resolutions of the City are enforced.
\subsubsection*{Subdivision 3.}
The City Administrator shall appoint and may suspend, remove, promote, demote, transfer and otherwise discipline upon the basis of merit and fitness and subject to applicable personnel rules, all subordinate officers and City employees, except that the approval of the Council shall be necessary before any such action affecting heads of departments shall be effective.
\subsubsection*{Subdivision 4.}
The City Administrator shall direct and supervise all departments, offices and agencies of the City, except as otherwise provided by law or Charter.
\begin{enumerate}
    \item Administration Department;
    \item Clerk-Treasurer Department;
    \item Fire Department/Emergency Management/Building Inspector;
    \item Police Department;
    \item Public Works Department;
    \item Community Development Department;
    \item Information Technology Department;
    \item Airport;
    \item City Attorney;
    \item Financial Advisor/Bond Consultant; and
    \item City Engineer Consultant.
\end{enumerate}
\subsubsection*{Subdivision 5.}
The City Administrator or the City Administrator’s designee shall attend all meetings of the Council and may take part in discussion but not vote. The Council may, in it’s discretion, exclude the City Administrator from any meetings at which the employment terms and conditions, removal, suspension or other discipline of the City Administrator is considered.
\subsubsection*{Subdivision 6.}
The City Administrator shall recommend to the Council for adoption such measures as the City Administrator deems necessary for the welfare of the people and the efficient administration of the City’s affairs.
\subsubsection*{Subdivision 7.}
The City Administrator shall keep the Council fully advised on the financial condition and needs of the City, and shall prepare and submit to the Council the annual budget and capital plan.
\subsubsection*{Subdivision 8.}
The City Administrator shall submit to the Council and make available to the public a complete report on the finances and administrative activities of the City at the end of each fiscal year.
\subsubsection*{Subdivision 9.}
The City Administrator shall assist the Council with long term and strategic planning.
\subsubsection*{Subdivision 10.}
The City Administrator shall perform such other duties as are prescribed by Charter or may be required by the Council.
\subsubsection*{Section 5.03, Administrative Organization.}
The Council may by ordinance establish City departments, offices and agencies and prescribe their functions. No power or duty conferred by this Charter upon a particular office or agency shall be transferred to any other.
\subsubsection*{Section 5.04, Subordinate Officers.}
There shall be a Clerk, Treasurer and such other subordinate officers to the City Administrator as the Council may establish by ordinance. The Clerk and Treasurer shall be subject to the direction of the City Administrator and shall have such duties as the Council may prescribe. The Council may by ordinance abolish offices which have been created by ordinance and it may combine the duties of various offices.
\subsubsection*{Section 5.05, Purchase And Contracts.}
The City Administrator shall be the chief purchasing agent of the City. All City purchases and contracts shall be made or let by the City Administrator when the amount involved does not exceed any limit set by Council resolution. All other purchases shall be made and all contracts let by the Council after the recommendation of the City Administrator has first been obtained. All purchase contracts above the amount set by Council resolution, all other contracts, bonds and instruments of any kind to which the City is a party shall be signed by the Mayor and the City Administrator on behalf of the City and shall be executed in the name of the City. The Council may, by ordinance, adopt further regulations for the making of bids and the letting of contracts including, but not limited to, regulations authorizing life cycle or total cost bidding.
