\chapter*{Chapter 120: \\
	Display, Sale, Storage, Possession and Use of Fireworks}
    \addstarredchapter{Chapter 120: Display, Sale, Storage, Possession and Use of Fireworks}
    \vfill
    \minitoc
    \emph{\textbf{Cross-Reference:}\\
        {\indent}Chapter 130: General Offenses, see Section 130.01}\\
    \indent\emph{\textbf{References:}\\
        {\indent}City of Crookston 1986 Code, Chapter 10, Section 10.10: Dangerous Weapons and Articles\\
        {\indent}Minnesota State Statutes 624 Subsections 624.20 through 624.25\\
        {\indent}Consumer Product Safety Commission Standards 16 CFR 1500 and 16 CFR 1507\\
        {\indent}Department of Transportation Requirement 49 CFR 170-173\\
        {\indent}Bureau of Alcohol Tobacco and Firearms Requirement 27 CFR 55}
    \pagebreak

\section{Purpose}
Due to the inherent risks of fire and injury to persons and property associated with the display, sale, possession and use of fireworks, the City Council has determined that it is necessary and in the interest of public health, safety and welfare to establish reasonable regulations concerning fireworks.
\section{Definition}
For purposes of this ordinance, "consumer fireworks" are defined as: Wire or wood sparklers of not more than 100 grams of mixture per item, other sparkling items which are non-explosive and non-aerial and contain 75 grams or less of chemical mixture per tube or a total of 200 grams or less for multiple tubes, snakes, and glow works, smoke devices, or trick noisemakers which include paper streamers, paper poppers, string poppers, snappers, and drop pops, each consisting of not more than twenty-five hundredths grains of explosive mixture.
\section{Possession and Sale of Fireworks}
\subsection{}
Fireworks are regulated by Minnesota Statutes 624.20 through 624.25 inclusive, which are adopted herein by reference. In addition to theses state laws, all display, sales, storage, and use of fireworks shall comply with this Section.
\subsection{}
No Person shall do any of the following without obtaining a City license:
\begin{enumerate}[{\indent}1)]
    \item A license must be applied for and approved prior to storing or selling any fireworks. 
    \item A permit must be applied for and approved 15 days prior to making a public display of fireworks. 
\end{enumerate}
\section{License Provisions}
Sale and/or Storage of Fireworks: It is unlawful for any person to sell, offer for sale, expose for sale, sell at retail or wholesale or store any consumer fireworks in the City of Crookston without a City license.
\section{License Application}
\subsection{}
The application for a license to store or sell fireworks shall be made to the City Clerk's office. The applicant shall completely fill out and submit an application for a consumer fireworks license prepared by the City of Crookston Clerk in conjunction with the Crookston Fire Department.  
\subsection{}
Information to be submitted as part of the license application includes, but is not necessarily limited to the following information:  
\begin{enumerate}[{\indent}1)]
    \item Name, address and telephone number of the applicant. 
    \item Address of location where the fireworks will be sold. 
    \item A list of fireworks that will be sold. The list must include the name, weight and quantity of fireworks, Tier II Material Safety Data Sheets. 
    \item Quantity of the fireworks that will be stored on the premises. 
    \item A floor plan designating the area where the fireworks will be sold and/or stored. 
    \item A letter of approval from the property owner, if different from the applicant. 
\end{enumerate}
\subsection{}
Prior to the issuance of a license, the premises must be inspected and approved by the Crookston Fire Department.
\section{Conditions of License}
A license to sell consumer fireworks shall be issued subject to the following conditions:
\begin{enumerate}[{\indent}A)]
    \item The license is non-transferable, either to a different person or location.
    \item The license must be publicly displayed on the licensed premises.
    \item The premises are subject to inspection by the Crookston Fire Department during normal business hours.
    \item The premises for which a license will be issued must be located in a zoning district permitting retail sales.
    \item Storage of consumer fireworks on the premises must be in compliance with the International Fire Code.
    \item The storage and/or retail sales of fireworks in a non-permanent structure shall be conducted in compliance with NFPA 1124.
    \item For transient sales of fireworks a license must be obtained according to Chapter 120.05 of the City Code.
    \item The licensee shall keep two (2) 2 $\frac{1}{2}$ gallon water type portable fire extinguishers within 15 feet of the storage and display areas.
    \item A list of all fireworks displayed for sale and stored on the property must be posted in a conspicuous location near the display/storage area. The list shall include the name, weight and quantity of fireworks and be accompanied by the Tire II Material Safety Data Sheets.
    \item No smoking shall be conducted within 50 feet of the consumer fireworks retail area.
    \item The Licensee shall prominently post "No Smoking" signs.
    \item The discharge of fireworks shall be prohibited within (100) feet of any location in which fireworks are being sold or stored.
    \item In buildings without an approved automatic sprinkler system, fireworks sales displays and/or storage shall be limited to fifty (50) lbs. net pyrotechnic composition or (200) lbs. gross weight, if the pyrotechnic composition weight is not known. In buildings with approved automatic sprinkler systems the quantity limits can be doubled.
\end{enumerate}
\section{License Bond}
Applicant shall file with the application a certificate of insurance, showing liability insurance coverage in the amount of \$1,000,000 per occurrence to cover Licensee's intentional and negligent acts relative to the sale, possession or use of fireworks.  Such insurance certificate shall indicate that the City of Crookston shall receive notice at least thirty days prior to cancellation or termination of the coverage.
\section{License Fee}
The annual license fee for the sale of fireworks shall be set by resolution by the City Council. See Fee Schedule.
\section{License Denial, Suspension and Revocation}
A consumer fireworks license may be denied, suspended or revoked by the City Council if a provision of the Chapter is violated.
\section{Permit Provisions}
No Person shall do any of the following without obtaining a city permit:
\begin{enumerate}[{\indent}A)]
    \item Public display of fireworks/pyrotechnic special effects; It is unlawful for any person to conduct a public pyrotechnic display in the City of Crookston without a city permit.
\end{enumerate}
\section{Permit Application}
\subsection{}
The application for a permit to conduct a public pyrotechnic display in the City of Crookston shall be made to the City Clerk's office. The applicant shall completely fill out and submit an application to conduct a public pyrotechnic display prepared by the City of Crookston Clerk in conjunction with the Crookston Fire Department.
\subsection{}
Information to be submitted as part of the permit application includes, but is not necessarily limited to the following information:
\begin{enumerate}[{\indent}1)]
    \item Name of applicant (Sponsoring Organization), address and telephone number of the applicant. 
    \item Name of authorized agent of applicant. 
    \item Name of supervising agent. (MN state certified pyrotechnic operator) 
    \item Date, time and location of display. (indoor display requires State Fire Marshall approval) 
    \item Manner and place of storage of fireworks/pyrotechnic special affects prior to use. 
    \item Type and number of fireworks/pyrotechnic special affects to be discharged.  The list must include number and size. 
    \item Names and birthdates of all assistants that will be participating in display. 
    \item Proof of a bond or insurance in the amount of at least 
    \item A diagram of the ground, or facilities at which the display will be held. 
    \item A letter of approval from the property owner, if different from the applicant. 
\end{enumerate}
\subsection{}
Prior to the issuance of a permit, the area of display must be inspected and approved by the Crookston Fire Department.
\section{Conditions of Permit}
A permit to display fireworks/pyrotechnic special affects shall be issued subject to the following conditions:
\begin{enumerate}[{\indent}A)]
    \item The permit is non-transferable, either to a different person or location. 
    \item The permit must be completed and returned at least 15 days prior to date of display. 
    \item All requests for changes (adding fireworks, etc.) must be approved in advance. All requests for changes must be submitted to the fire chief at least 24 hours prior to the display. 
    \item All displays are conducted in accordance with applicable laws, codes, regulations, and guidelines relating to fireworks. 
    \item Ensure local fire chief has been contacted about standby fire apparatus and personnel.
    \item Provide monitors around discharge site. 
    \item Provisions for crowd control. 
    \item A sufficient number of trained assistants are on hand. 
    \item Proper protective gear is worn by all personnel involved with the display. 
    \item Sufficient portable fire extinguishers must be present at the display site. 
    \item A written report of all injuries, fires, or unsafe products observed must be reported to the local fire chief and State Fire Marshall within 10 days of the display. 
    \item Smoking and open flames are prohibited within 50 feet of the aerial shell storage area.  NO SMOKING OR OPEN FLAME signs must be conspicuously posted in the area.
    \item Operators and attendants must use only flashlights or electric lighting for artificial illumination.  
    \item Fireworks must not be left unattended or allowed to become wet at the display site. 
    \item If the local fire chief or pyrotechnic operator determines that there is a lack of crowd control or that the crowd is in danger, the display must be immediately discontinued.  If at any time winds or wet weather create a danger the display must be postponed until conditions are acceptable to the fire chief. 
    \item The entire firing range must be inspected immediately following a display and prior to allowing public access for the purpose of locating unexploded aerial shells. 
\end{enumerate}
\section{Permit Bond}
Applicant shall file with the application a certificate of insurance, showing liability insurance coverage in the amount of \$1,000,000 per occurrence to cover Licensee's intentional and negligent acts relative to the sale, possession or use of fireworks. Such insurance certificate shall indicate that the City of Crookston shall receive notice at least thirty days prior to cancellation or termination of the coverage.
\section{Permit Fee}
The permit fee for the public display of fireworks shall be set by resolution by the City Council. See Fee Schedule.
\section{Permit Denial, Suspension and Revocation}
\subsection{}
A consumer fireworks license may be denied, suspended or revoked by the City Council if a provision of the Chapter is violated.
\subsection{}
It shall be unlawful to do any of the following:
\begin{enumerate}[{\indent}1)]
    \item Consumer fireworks shall not be used within one hundred (100) feet of any building in which fireworks are sold or stored.
    \item Consumer fireworks shall not be sold or distributed to persons under the age of eighteen (18) years, any person who is obviously intoxicated, chemically impaired or incompetent, or any person who fails to present proper age identification.
    \item Consumer fireworks shall not be used indoors.
    \item Consumer fireworks shall not be used on public property.  Fireworks shall not be discharged along a parade route prior to, during or after any parade, or at any place of public assembly, park, or government property except such discharge of fireworks may be permitted in connection with an officially sanctioned public celebration.
    \item Consumer fireworks shall not be thrown or tossed at any person, animal, vehicle, or other thing or object.
    \item The Fire Chief may ban fireworks for any period of time for any public safety reason.
\end{enumerate}
\section{A Violation of this Section is a Misdemeanor}
Fireworks that are kept possessed or stored in violation of state statutes or of this section may be confiscated and destroyed.  The costs associated with disposal shall be paid by the violator and/or be assessed back to the property on which the fireworks are being stored, displayed or sold.
