\chapter*{Chapter 95: \\
	Parks and Recreation}
    \addstarredchapter{Chapter 95: Parks and Recreation}
    \vfill
    \minitoc
    \pagebreak

\subchapter{PARK REGULATIONS}

\setcounter{section}{24}
\section{Violation}
\index{PARKS AND RECREATION!PARK REGULATIONS!Violation}
It is unlawful for any person to, in any public park or recreation area, violate any of the following regulations contained in SEC. 95.26 through SEC. 95.35.\footnote{(‘83 Code, SEC. 10.13)  Penalty, see SEC. 10.99}

\section{Allowable Hours of Use}
\index{PARKS AND RECREATION!PARK REGULATIONS!Allowable Hours of Use}
Public parks and recreation areas shall not be occupied or used between 10:00 p.m. and 6:00 a.m. of the following day, except the camping area, or except by a special permit issued by the Park Director.\footnote{(‘83 Code, SEC. 10.13, Subd. 8) Penalty, see SEC. 10.99}

\section{Weapons, Gambling, Alcoholic Beverages and Indecent Conduct Prohibited}
\index{PARKS AND RECREATION!PARK REGULATIONS!Weapons, Gambling, Alcoholic Beverages and Indecent Conduct Prohibited}
\subsection{}
No firearms, air rifles, BB guns, sling shots, explosives or fireworks shall be brought into or used in park areas, unless authorized by the Director of Parks and Recreation.
\subsection{}
Gambling, excessive use of alcoholic beverages, or abusive, boisterous, profane, or indecent language, conduct, or attire will not be allowed.\footnote{(‘83 Code, SEC. 10.13, Subds. 1, 2)  Penalty, see SEC. 10.99}

\section{Advertising, Distribution of Literature Prohibited}
\index{PARKS AND RECREATION!PARK REGULATIONS!Advertising, Distribution of Literature Prohibited}
\subsection{}
No unauthorized advertising, selling, or solicitation is allowed in parks or recreation areas.
\subsection{}
Distribution or display of obscene literature is prohibited in all parks and recreation areas.
\subsection{}
Placing of advertising, decorations or other devices of any kind on vases, statues, flagpoles, monuments or structures is prohibited.\footnote{(‘83 Code, SEC. 10.13, Subds. 3, 13, 16)  Penalty, see SEC. 10.99}

\section{Control of Dogs and Pets; Noninterference with Wildlife}
\index{PARKS AND RECREATION!PARK REGULATIONS!Control of Dogs and Pets; Noninterference with Wildlife}
Dogs and pets must be kept under control.  Wildlife must not be molested, disturbed or injured.\footnote{(‘83 Code, SEC. 10.13, Subd. 4)  Penalty, see SEC. 10.99}

\section{Games, Picnicking and Fires}
\index{PARKS AND RECREATION!PARK REGULATIONS!Games, Picnicking and Fires}
\subsection{}
Active games must be limited to designated play areas.
\subsection{}
Picnicking and fires are allowed in designated areas only.  Fires must be attended at all times and extinguished after use.\footnote{(‘83 Code, SEC. 10.13, Subds. 5, 7)  Penalty, see SEC. 10.99}

\section{Traffic and Parking Regulations}
\index{PARKS AND RECREATION!PARK REGULATIONS!Traffic and Parking Regulations}
Motorists will observe speed limits and drive on designated roadways only as posted, and park in designated areas.\footnote{(‘83 Code, SEC. 10.13, Subd. 6)  Penalty, see SEC. 10.99}

\section{Dumping Refuse, Depositing Matter in Ponds, and the Like}
\index{PARKS AND RECREATION!PARK REGULATIONS!Dumping Refuse, Depositing Matter in Ponds, and the Like}
\subsection{}
Dumping or depositing bottles, broken glass, ashes, paper, boxes, cans or refuse of any kind is prohibited except in the containers provided in the parks.
\subsection{}
Discharge in waters of any pond, stream, or any other body of water, of any substance, or liquid, or solid, or any other matter or thing which will result in pollution of the water is prohibited.\footnote{(‘83 Code, SEC. 10.13, Subds. 9, 10)  Penalty, see SEC. 10.99}

\section{Damaging or Tampering with Park Property}
\index{PARKS AND RECREATION!PARK REGULATIONS!Damaging or Tampering with Park Property}
\subsection{}
Removal, breaking, destruction, injury, mutilation, or defacement in any way of any structure, monument, statue, vase, fountain, fence, railing, flag pole, vehicle, bench, tree, shrub, fern, plant, flower, fireplace or other property in any park is prohibited.
\subsection{}
Climbing of trees or flag poles, sitting or standing upon monuments, vases, fountains, railings or fences in any park or recreation area is prohibited.\footnote{(‘83 Code, SEC. 10.13, Subds. 11, 14)  Penalty, see SEC. 10.99}

\section{Solicitation for Immoral Purpose}
\index{PARKS AND RECREATION!PARK REGULATIONS!Solicitation for Immoral Purpose}
No person shall solicit the acquaintance of another in any park or recreation area for any immoral purposes.\footnote{(‘83 Code, SEC. 10.13, Subd. 12)  Penalty, see SEC. 10.99}

\section{Permit Required for Exclusive Use}
\index{PARKS AND RECREATION!PARK REGULATIONS!Permit Required for Exclusive Use}
No person or organization shall use a park or park area for group celebrations, meetings, entertainment, and the like, which are considered “exclusive use,” except through use of a permit issued by the Parks Director.\footnote{(‘83 Code, SEC. 10.13, Subd. 15)  Penalty, see SEC. 10.99}
