\chapter*{Chapter 32: \\
	Departments, Boards and Commissions}
    \addstarredchapter{Chapter 32: Departments, Boards, and Commissions}
%    \index{DEPARTMENTS, BOARDS, AND COMMISSIONS}
    \index{BOARDS|see{DEPARTMENTS, BOARDS, AND COMMISSIONS}}
    \index{COMMISSIONS|see{DEPARTMENTS, BOARDS, AND COMMISSIONS}}
    \vfill
    \minitoc
    \pagebreak

\subchapter{GENERAL PROVISIONS}
\section{Departments Generally}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!GENERAL PROVISIONS!Departments Generally}
\subsection{Control}
All departments of the city are under the overall control of the City Administrator. Heads of all departments are responsible to the City Administrator and subject to his or her supervision and direction, except as otherwise provided herein.
\subsection{Appointment}
All department heads shall be appointed by the Council, except those as are created under statute. All appointments shall be for an indeterminate term and subject to any applicable civil service regulations in effect in the city.
\subsection{Compensation}
All wages and salaries shall be fixed and determined by the Council.
\subsection{Table of Organization and Lines of Responsibility.}
The Council may by resolution adopt, amend, and from time to time revise, a table of organization and define lines of responsibility and authority for the efficient governmental organization of the city.
\subsection{Budgetary Information}
The City Administrator shall keep the Council fully advised on the financial condition and needs of the city, and shall prepare and submit to the Council the annual budget and capital plan.

\section{Boards and Commissions Generally}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!GENERAL PROVISIONS!Boards and Commissions Generally}
\subsection{}
All Board and Commission appointments authorized by ordinance or resolution shall be made by the Mayor, brought to the Ways and Means Committee for approval, and the appointment confirmed by the Council at the first regular meeting in January of each year.  The term of each appointee shall be established and stated at the time of appointment, and terms of present Board and Commission members may be re-established and changed to give effect to this section. No Board or Commission member shall be appointed to more than two full consecutive terms. Terms of elected officials serving on a Board or Commission shall coincide with their term of office as members of the City Council. New appointees shall assume office on January 1, December 31 being the date of expiration of terms. Provided, however, that all appointees to Boards and Commissions shall hold office until their successor is appointed and qualified. All vacancies shall be filled in the same manner as for an expired term, but the appointment shall be effective immediately when made and only for the unexpired term.
\subsection{}
No appointed Board or Commission member shall be an employee of the city except those who are members by virtue of their office. All appointed Board and Commission members shall serve without remuneration, but may be reimbursed for out-of-pocket expenses incurred in the performance of their duties when the expenses have been authorized by the Council before they were incurred.
\subsection{}
The Chairman and Secretary shall be chosen from and by the Board or Commission membership at its first regular meeting in December of each year to serve for the next calendar year. Any Board or Commission member may be removed by the Council for misfeasance, malfeasance or non-feasance in office and his position filled as any other vacancy.
\subsection{}
The City Administrator shall be an ex officio member of all Boards and Commissions; provided, that if he or she is unable to attend a meeting or act in the capacity of membership, he or she may be represented by his or her assistant or some person duly authorized by him or her. Except as otherwise provided, this section shall apply to all Boards and Commissions.\\

\subchapter{ADMINISTRATION DEPARTMENT}
\setcounter{section}{9}
\section{Establishment}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!ADMINISTRATION DEPARTMENT!Establishment}
\subsection{}
An Administration Department is hereby established. The head of the Department shall be the City Administrator.
\subsection{}
The City Administrator shall be responsible to the City Council. The City Administrator shall also make and file reports as may be requested by the City Council.
\subsection{}
Powers and duties of the City Administrator are as presented in SEC. 31.01(B).\\

\subchapter{CLERK/TREASURER DEPARTMENT}
\setcounter{section}{19}
\section{Establishment}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!CLERK/TREASURER DEPARTMENT!Establishment}
\subsection{}
A Clerk/Treasurer Department is hereby established. The head of the Department shall be the Clerk/Treasurer.
\subsection{}
The Clerk/Treasurer shall be responsible to the City Administrator. The Clerk /Treasurer shall also make and file reports as may be requested by the City Administrator.\\

\subchapter{FIRE DEPARTMENT}
\setcounter{section}{39}
\section{Establishment}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!FIRE DEPARTMENT!Establishment}
\subsection{}
A Fire Department is hereby established.  The Fire Chief shall direct and supervise the Fire Department and be responsible to the City Administrator.
\subsection{}
The Chief of the Fire Department shall have general supervision of the Fire Department and custody of all property used and maintained for the purposes of the Fire Department.  The Chief shall see that the same are kept in proper order and that all rules and regulations and all provisions of the laws of the State of Minnesota and ordinance of the city relative to a Fire Department and prevention and extinguishment of fires are duly observed.  The Chief shall supervise the preservation of all property endangered by fire and shall control and direct all persons engaged in preserving property.  Building regulations are also administered by the Fire Department. In case of absence or disability of the Chief for any cause, the next in command shall exercise all powers, perform all the duties and be subject to all the responsibilities of the Chief.
\subsection{}
Chief of the Fire Department shall also make and file reports as may be requested by the Administrator.
\subsection{}
The Building Official shall enforce the building and zoning regulations of the city and shall perform all duties assigned as follows:
\begin{enumerate}
    \item Issue occupancy, building and other permits, and make and maintain records thereof.
    \item Conduct inspections of buildings and use of land to determine compliance with the terms of the city’s building and zoning regulations.
    \item Maintain permanent and current records, including, but not limited to, all maps, amendments, and conditional use permits, variances, appeals and applications thereof.
    \item Receive, file, and forward all applications for appeals, variances, conditional uses or other matters to the proper designated officials or bodies.
    \item Notify the City Attorney of any violations of the building and zoning regulations for appropriate action.
    \item The Fire Chief shall see that all rules and regulations and all provisions of the State of Minnesota and ordinances of the city relative to the operation of the Department are observed.
\end{enumerate}

\subchapter{INFORMATION TECHNOLOGY DEPARTMENT}
\setcounter{section}{49}
\section{Establishment}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!INFORMATION TECHNOLOGY DEPARTMENT!Establishment}
\subsection{}
An Information Technology Department is hereby established. The head of the Department shall be the Information Technology Director.
\subsection{}
The Information Technology Director shall be responsible to the City Administrator. The technology facilities and equipment, including, but not limited to, computer programming and maintenance, as well as electronic communications, shall be under the supervision and control of all property of the Department. The Director shall also make and file reports as may be requested by the City Administrator.\\

\subchapter{PARKS AND RECREATION DEPARTMENT}
\setcounter{section}{59}
\section{Establishment}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!PARKS AND RECREATION DEPARTMENT!Establishment}
\subsection{}
A Parks and Recreation Department is hereby established. The head of this Department shall be the Parks and Recreation Director. All park facilities and recreational programs and equipment shall be under the direct control of the Director.
\subsection{}
The Parks and Recreation Director shall be responsible to the City Administrator. The Parks and Recreation Director shall also make and file reports as may be requested by the City Administrator.\\

\subchapter{POLICE DEPARTMENT}
\setcounter{section}{69}
\section{Establishment}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!POLICE DEPARTMENT!Establishment}
\subsection{}
A Police Department is hereby established. The Chief of Police shall direct and supervise the Police Department and be responsible to the City Administrator.
\subsection{}
The Chief of the Police Department shall have general supervision of the Police Department and custody of all property used and maintained for the purpose of public safety.  The Chief shall see that the same are kept in proper order and that all rules and regulations and all provisions of the laws of the State of Minnesota and ordinances of the city relative to a Police Department are duly observed. The Chief of Police and all members of the Police Department shall have the powers and authority of police officers generally and shall perform the duties as are required of them by the law.
\subsection{}
It is the duty of the Chief of Police, on or before the first Council meeting of each month, to file with the City Administrator a report as to the activities of the Department during the previous month. The Chief of Police shall also make and file other reports as may be requested by the City Administrator.

\section{Police Reserve}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!POLICE DEPARTMENT!Police Reserve}
\subsection{}
A Police Reserve is hereby established.
\subsection{}
The purpose of this section is to provide assistance to the Police Department to ensure that the public peace, health and safety of the city is preserved.
\subsection{}
The functions of the Police Reserve are to provide supplementary assistance to the Police Department at special events, traffic or crowd control, and administrative or clerical assistance.
\subsection{}
The Police Reserve is under the direct supervision and control of the Chief of Police.  The Chief is responsible for the organization, administration, and operation of the Police Reserve, subject to the direction and control of the City Administrator. The Chief of Police may designate members of the Police Reserve to serve as officers of the Reserve. The Chief may, by order, establish rules and regulations to govern the Reserve including the fixing of specific duties of its members and providing for the maintenance of discipline.
\subsection{}
The Chief of Police is responsible for coordinating functions of the Police Reserve and the Police Department. The Chief will institute training programs and establish annual requirements as he or she deems necessary. The Chief is responsible for organizing the Police Reserve, selecting its personnel, determining the number of members in the Police Reserve and discharging any member of the Police Reserve for good cause. The Chief of Police will maintain an inventory of all equipment issued to the Police Reserve. All duties of the Chief of Police described in this division are subject to the direction and control of the Administrator.
\subsection{General Provisions for Police Reserve Members.}
\begin{enumerate}
    \item Members of the Police Reserve must be of good moral character.
    \item The Police Reserve is a volunteer organization and members are generally not compensated for their services. However, members may be compensated for certain duties, such as security for private and public events, dances, sporting events, transports, guarding prisoners in the hospital, or other special duties at the discretion of the Chief of Police.
    \item Members of the Police Reserve are covered by the provisions of the city Worker’s Compensation Insurance and Liability Insurance policies while on duty.
    \item Each Police Reserve member will be provided with suitable insignia or other identification as required by the Chief of Police.
    \item No Police Reserve member shall carry any firearm while on duty.
\end{enumerate}


\subchapter{PUBLIC WORKS DEPARTMENT}
\setcounter{section}{79}
\section{Establishment}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!PUBLIC WORKS DEPARTMENT!Establishment}
\subsection{}
A Public Works Department is hereby established.  The head of the Department shall be the Public Works Director who is responsible to the City Administrator.
\subsection{}
The Public Works Director shall be responsible for and have custody of all property of the Department, which shall include, but not necessarily be limited to, the city sewage systems, streets, refuse collection, water systems and engineering that shall be directed by the City Administrator.
\subsection{}
The Public Works Director shall be responsible for all city water facilities, including but not limited to, pumping, filtration, distribution lines, and connections therewith, shall be under the direct supervision and control of the Director and the Director shall be responsible for and have custody and control of all property of the Department.
\subsection{}
It is also the duty of the Public Works Director, on or before the first regular Council meeting of each month, to file with the City Administrator a report as to the activities of the Department during the preceding month.  The Director shall also make and file other reports as may be requested by the City Administrator.\\

\subchapter{AIRPORT COMMISSION}
\setcounter{section}{99}
\section{Creation, Appointment, and Compensation}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!AIRPORT COMMISSION!Creation, Appointment, and Compensation}
\subsection{Creation}
Pursuant to the applicable Minnesota Statutes, there is hereby created an Airport Commission composed of five members.
\subsection{Appointment and Compensation}
The members of the Commission shall be appointed by the Mayor and all appointments shall be confirmed by a majority vote of the Council.  Members shall serve without compensation.

\section{Term; Officers}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!AIRPORT COMMISSION!Term; Officers}
\subsection{Term of Office}
The term of office shall be three years with the terms staggered.  The term of office shall expire on the first Monday in January of each year.  Provided, however, that one member may be selected by the Council from its membership.
\subsection{Officers}
The Commission shall elect one of its members to be Chairperson of the Commission, and one member thereof to be Vice-Chairperson.  The Clerk-Treasurer shall be the Treasurer of the Commission.  The officers so elected shall hold office for a term of one year and until their successors are appointed and qualified.  The Commission may select from its membership one member to serve as Secretary, or may select a non-member to serve as Secretary.

\section{Powers and Duties}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!AIRPORT COMMISSION!Powers and Duties}
The Commission shall have the authority and responsibility for the construction, enlargement, maintenance, equipment, operation and regulation of the Municipal Airport, also known as the Kirkwood Airport, as may be vested in the city under the laws of the State of Minnesota and of the United States relating to the construction, management and operation of the airport, except as mentioned herein.
\subsection{}
The Commission may exercise, on behalf of the city, all the powers granted to the city by Minnesota Statutes, provided:
\begin{enumerate}
    \item Real property, airports, restricted landing areas, airport protection privileges or personal property costing in excess of a sum to be set by the city may be acquired and condemnation proceedings may be instituted, only by authority of the Council.  All rules and regulations provided for by M.S. SEC. 360.038, Subd. (3), as it may be amended from time to time, shall be effective only upon approval of the Council.
    \item No real property and no airports, other air navigation facilities or air protection privilege shall be disposed of by the Commission, by sale, lease, or otherwise, except by authority of the Council, but the Commission may lease space, area or improvements and grant concessions for aeronautical purposes or purposes incidental thereto, subject to the provisions of M.S. SEC. 360.038, Subd. (4), as it may be amended from time to time.
\end{enumerate}
\subsection{}
The Commission shall have authority to hire or retain employees and professional services as may be necessary to accomplish the purposes for which it was appointed, and to fix any salaries.
\subsection{}
The Commission shall keep and maintain full and complete financial records.  The Commission shall maintain a current inventory of all airport property showing the approximate date acquired and the cost thereof.

\section{Budget; Annual Report}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!AIRPORT COMMISSION!Budget; Annual Report}
\subsection{Budget}
The Commission each year at the appropriate time shall prepare a budget for financing the airport for the ensuing year which shall be furnished to the Council.  Final decision as to requested appropriations shall be reported to the Commission which shall adjust its budget if necessary so that its budget at all times shall be balanced.  Money not expended shall be credited to the surplus of the Airport Fund.
\begin{enumerate}
    \item The Commission shall control the expenditures of all monies collected for or placed to the credit of the Airport Fund.  All monies received shall be paid to the city treasury, credited to the Airport Fund and kept separately from other monies of the city and paid out only upon itemized vouchers approved by the Commission.
    \item The Commission shall have no power to levy taxes or borrow money and it shall not approve any claim or incur any obligations for expenditures unless there is unencumbered cash in the appropriate Airport Fund to the credit of the Commission with which to pay the same.
\end{enumerate}
\subsection{Report of Commission}
The Commission, as soon as possible after the end of each calendar year, shall prepare and present to the Council a report of its activities and finances.  The Commission shall also prepare and present federal and state officials with reports as may be required by law, regulation or contract.\\

\subchapter{CHARTER COMMISSION}
\setcounter{section}{109}
\section{Establishment and Composition}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!CHARTER COMMISSION!Establishment and Compensation}
A Charter Commission is hereby established. The Commission shall be composed of twelve members, who shall serve staggered four-year terms.  The City Attorney, by reason of their position, shall be an ex officio member. The Mayor and Council shall make all appointments.

\section{Powers and Duties}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!CHARTER COMMISSION!Powers and Duties}
The Charter Commission shall have all the powers and duties defined or granted in the statutes and the city code and shall act in an advisory capacity to the Council.\\

\subchapter{PLANNING COMMISSION}
\setcounter{section}{119}
\section{Establishment and Composition}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!PLANNING COMMISSION!Establishment and Composition}
A Planning Commission is hereby established.  The Commission shall be composed of five members, four of whom shall serve staggered four-year terms.  The City Attorney and a member of the City Council, by reason of their positions, shall be ex officio members.  The Mayor and Council shall make all appointments.

\section{Powers and Duties}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!PLANNING COMMISSION!Powers and Duties}
The Planning Commission shall have all the powers and duties defined or granted in the statutes and the city code relating to planning, zoning and subdivision regulations and shall act in an advisory capacity to the Council in all of these areas.\\
The Planning Commission shall provide assistance to the Council and Zoning Administrator in the administration of this chapter and the recommendation of the Planning Commission shall be advisory in nature. Specifically, the Planning Commission shall review, hold public hearings, and make recommendations to the Council on all applications for zoning amendments, variances, and conditional use permits using the criteria in SEC. 152.198 through SEC. 152.200 of this chapter.

\subchapter{BOARD OF ZONING APPEALS}
\setcounter{section}{129}
\section{Establishment and Composition}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!BOARD OF ZONING APPEALS!Establishment and Composition}
A Board of Zoning Appeals is hereby established, which shall consist of the Council, vested with the administrative authority as hereinafter provided.

\section{Powers and Duties}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!BOARD OF ZONING APPEALS!Powers and Duties}
\subsection{}
The Board of Zoning Appeals shall act upon all questions as they may arise in the administration of this chapter, including the interpretation of zoning maps, and it shall hear and decide appeals from and review any order, requirement, decision, or determination made by the Zoning Administrator. The appeal may be taken by any person, firm, or corporation aggrieved or by any officer, department, board or bureau of the city. The Board of Zoning Appeals shall also have the power to grant variances to the provisions of this chapter under certain conditions indicated in SEC.152.200 of this chapter. No use variances; a use different than that allowed in the zoning district, shall be issued by the Board of Zoning Appeals.
\subsection{}
Meetings by the Board of Zoning Appeals shall be held within the time and upon the notice to interested parties as is provided in this chapter and its adopted rules for the transaction of its business. The Board shall, within 60 days after receiving a request for a variance, refer the proposed variance to the Planning Commission for review and comment. After receiving the comments of the Planning Commission, the Board shall make its order deciding the matter, and shall serve a copy of the order upon the appellant or petitioner by mail. Any party may appear at the meeting in person or by agent or attorney. The Board of Zoning Appeals may reverse or affirm wholly or partially, or may modify the order, requirement, decision, or determination as in its opinion ought to be made and to that end shall have all the powers of the officer from whom the appeal was taken and may issue or direct the issuance of a permit. The reasons for the decision shall be stated and recorded.  The decision of the Board shall not be final and any person having an interest affected by the decision shall have the right to appeal to District Court in the county in which the land is located on questions of law and fact. A vote of the majority of the Board of Zoning Appeals shall be necessary to reverse any decision of an administrative official of the city or to decide in favor of the applicant.\\

\subchapter{LIBRARY BOARD}
\setcounter{section}{139}
\section{Establishment and Composition}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!LIBRARY BOARD!Establishment and Composition}
A Library Board is hereby established. The Board shall be composed of five members, who shall serve staggered three-year terms. The Mayor and Council shall make all appointments.

\section{Powers and Duties}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!LIBRARY BOARD!Powers and Duties}
The Library Board shall have all the powers and duties defined or granted in the statutes and the city code relating to the public library (Lake Agassiz Regional Library) and shall act in an advisory capacity to the Council.\\

\subchapter{PARK BOARD}
\setcounter{section}{149}
\section{Purpose; Creation of Board}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!PARK BOARD!Purpose; Creation of Board}
\subsection{Purpose}
The nature and operation of the various parks and recreation programs of the city are uniquely allied with individual citizens. Therefore, it is in the best interests of the city and its citizens that concentration of public opinion and decision-making pertaining to city parks and recreation originate with a citizens’ board established for that purpose.
\subsection{Creation of Board}
There is hereby created the Parks and Recreation Board which, for the purposes of this subchapter, is referred to as the Board.

\section{Authority and Duties}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!PARK BOARD!Authority and Duties}
Subject to the reservation of powers set forth in SEC. 32.153, the Board has the following duties and powers:
\subsection{}
Establish policy for the creation, operation, maintenance and discontinuance of city parks and recreation programs;
\subsection{}
Serve as a forum for consideration, study and response to city concerns relating to parks and recreation programs and services;
\subsection{}
Establish goals and objectives for the Parks and Recreation Department;
\subsection{}
Determine facility and equipment needs;
\subsection{}
Evaluate community needs and desires for recreational programs and leisure activities;
\subsection{}
Evaluate existing facilities and programs;
\subsection{}
Develop and revise park and recreation policies;
\subsection{}
Take steps to learn the opinion of the public on parks and recreation needs by means of public hearings, surveys, informal advisory elections or by any other method which will obtain opinions from the public;
\subsection{}
Develop an annual budget for the Parks and Recreation Department which shall be included unchanged in the city’s proposed budget submitted to the Council by the City Administrator unless the City Administrator attaches to the proposed budget a written explanation of each variance therefrom, along with the City Administrator’s reason(s) for the variance;
\subsection{}
Develop a five-year capital improvement plan for the Parks and Recreation Department which shall be included unchanged in the city’s proposed five-year capital improvement plan submitted to the Council by the City Administrator unless the City Administrator attaches to the proposed plan a written explanation of each variance therefrom, along with the City Administrator’s reason(s) for the variance; and
\subsection{}
In the name of the city, approve all contracts, leases, acquisitions and disposals of property, debts, obligations, liabilities and expenditures for park and recreation purposes, provided that all purchases and contracts must be made consistent with Section 5.05 of the City Charter and no such action may be approved by the Board which cannot, at the time it is approved, be paid for in full from actual resources appropriated for the specific purpose for which the action is undertaken pursuant to a budget adopted or amended by the Council.

\section{Personnel; Membership and Organization}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!PARK BOARD!Personnel; Membership and Organization}
\subsection{}
The Board, either for itself or on behalf of the city, shall have no power to employ, compensate or control employees. The Board may deal with city administrative officers and employees solely through the City Administrator and, with the City Administrator’s permission, the Parks and Recreation Director. The City Administrator shall act as the purchasing agent for the Board.
\subsection{}
The membership and organization of the Board shall be as follows:
\subsubsection{Membership}
The Board shall consist of five members, no more than one of which may be a Council member. Board members shall be appointed by the Mayor with the consent of the Council.
\subsubsection{Term}
A member of the Board shall serve a term of three years or until the member’s successor is appointed and qualified. No member shall serve for more than two successive full terms.  Any person appointed as a member of the Board who was, as of December 31, 1999, a member of the Park Board shall serve out the term that the member then had; and the fact that the member has served on the Park Board and the Board through and up to the time of the member’s appointment shall be taken into account for the purpose of term limitation. The remainder of the persons initially appointed as Board members shall, by designation of the Mayor as part of the Mayor’s appointment, serve staggered terms so that the terms of no more than two members of the Board expire each calendar year.
\subsubsection{Vacancies}
Vacancies on the Board shall be filled in the same manner that original appointments are made. Any member who misses three or more consecutive meetings without an excuse approved by the Board shall be deemed to have vacated his or her office and the vacancy shall be filled in the manner provided for filling vacancies.
\subsubsection{Removal}
If the Council determines that a member of the Board has not performed his or her duties in accordance with the purposes of this subchapter or has been guilty of nonfeasance or malfeasance in office, the member shall be replaced in the manner for filling a vacancy.
\subsubsection{Meetings}
The Board shall hold regular meetings at least quarterly.  Special meetings may be called by the Chairperson or by any two members, by written notice as required by law for city meetings.  Meetings of the Board shall be subject to the Open Meeting Law.
\subsubsection{Compensation}
Members of the Board shall serve without pay, but they may be reimbursed for actual out-of-pocket expenses.
\subsubsection{Officers}
The members of the Board shall select one of their members as Chairperson and one of their members as Secretary.  The Clerk-Treasurer shall act as Treasurer of the Board.
\subsubsection{Quorum and Voting}
A vote of at least three members shall be required to pass any measures.  Three members of the Board shall constitute a quorum.

\section{Reservation of Powers}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!PARK BOARD!Reservation of Powers}
If there is a conflict between a provision of this subchapter and a provision of the City Charter, the City Charter provision shall prevail.  All powers and duties of the Council and the City Administrator set forth in the City Charter are preserved. However, the Council shall not, except by an affirmative vote of at least five Council Members, or four Council Members and the Mayor or the Assistant Mayor in the event of a tie, take any action relating to parks and recreation which has not first been approved or recommended by the Board or which has not been appealed from a Board action or decision.

\section{Appeal to Council}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!PARK BOARD!Appeal to Council}
Any person aggrieved by any action or decision of the Board may appeal the action or decision to the Council by filing a notice of appeal, in writing, with the Clerk-Treasurer within ten days of the action or decision.  The Council shall then consider the action or decision and a determination by the Council thereon shall be final.  The appealed action or decision shall remain effective pending appeal unless it is suspended by order of the Council.

\section{Amendment}
\index{DEPARTMENTS, BOARDS, AND COMMISSIONS!PARK BOARD!Amendment}
Like other ordinances, this subchapter may be repealed or amended, in whole or in part, by further action of the Council in the manner provided for the passage of ordinances in the City Charter.
