\chapter*{Chapter 10: \\
	General Provisions}
    \addstarredchapter{Chapter 10: General Provisions}
    \vfill
    \minitoc
    \pagebreak

\section{Title of Code}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Title of Code}
\subsection{}
All ordinances of a permanent and general nature of the city, as revised, codified, rearranged, renumbered, and consolidated into component codes, titles, chapters, and sections, shall be known and designated as the “city code,” for which designation “code of ordinances,” “codified ordinances” or “code” may be substituted.  Code title, chapter, and section headings do not constitute any part of the law as contained in the code.
\subsection{}
All references to codes, titles, chapters, and sections are to the components of the code unless otherwise specified.  Any component code may be referred to and cited by its name, such as the “Traffic Code.”  Sections may be referred to and cited by the designation “SEC.” followed by the number, such as “SEC. 10.01.”


\section{Rules of Interpretation}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Rules of Interpretation}
\subsection{Generally}
Unless otherwise provided herein, or by law or implication required, the same rules of construction, definition, and application shall govern the interpretation of this code as those governing the interpretation of state law.
\subsection{Specific Rules of Interpretation}
The construction of all ordinances of this city shall be by the following rules, unless that construction is plainly repugnant to the intent of the legislative body or of the context of the same ordinance:
\subsubsection{AND or OR}
Either conjunction shall include the other as if written “and/or,” whenever the context requires.
\subsubsection{Acts by Assistants}
When a statute, code provisions or ordinance requires an act to be done which, by law, an agent or deputy as well may do as the principal, that requisition shall be satisfied by the performance of the act by an authorized agent or deputy.
\subsubsection{Gender; Singular and Plural; Tenses}
Words denoting the masculine gender shall be deemed to include the feminine and neuter genders; words in the singular shall include the plural, and words in the plural shall include the singular; the use of a verb in the present tense shall include the future, if applicable.
\subsubsection{General Term}
A general term following specific enumeration of terms is not to be limited to the class enumerated unless expressly so limited.


\section{Application of Future Ordinances}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Application of Future Ordinances}
All provisions of Title I compatible with future legislation shall apply to ordinances hereafter adopted which amend or supplement this code unless otherwise specifically provided.


\section{Captions}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Captions}
Headings and captions used in this code other than the title, chapter, and section numbers are employed for reference purposes only and shall not be deemed a part of the text of any section.


\section{Definitions}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Definitions}
\subsection{General Rule}
Words and phrases shall be taken in their plain, or ordinary and usual sense.  However, technical words and phrases having a peculiar and appropriate meaning in law shall be understood according to their technical import.
\subsection{Definitions}
For the purpose of this code, the following definitions shall apply unless the context clearly indicates or requires a different meaning.
\begin{description}
\item[CITY] The area within the corporate boundaries of the city as presently established or as amended by ordinance, annexation or other legal actions at a future time.  The term \textbf{CITY} when used in this code may also be used to refer to the City Council and its authorized representatives.
\item[CITY ADMINISTRATOR or ADMINISTRATOR] The person duly appointed by the City Council as City Administrator and acting in that capacity as the Chief Administrative Officer (see Section 5.01 of the City Charter).
\item[CITY CLERK-TREASURER] The person duly appointed by the City Council and acting in that capacity.
\item[CITY COUNCIL or COUNCIL] The City Council of the City of Crookston, Minnesota.
\item[CODE, THIS CODE, or THIS CODE OF ORDINANCES] This city code as modified by amendment, revision, and adoption of new titles, chapters, or sections.
\item[CONVICTION] Either of the following accepted and recorded by the court:
\newline\indent
(a) A plea of guilty; or
\newline\indent
(b) A verdict of guilty by a jury or a finding of guilty by the court.
\item[COUNTY] The county or counties in which the city is located.
\item[CRIME] Conduct which is prohibited by ordinance and for which the actor may be sentenced to imprisonment or fine.
\item[EX OFFICIO MEMBER] A person who is not counted for the purposes of determining a quorum and has no right to vote, but shall have the right and obligation (within discretion) to speak to any question coming before the board, commission or other deliberative body of which they are a member.
\item[INTERSECTION] The area embraced within the prolongation or connection of the lateral curb line or, if no curb, then the lateral boundary lines of the roadways or streets, which join one another at, or approximately at, right angles; or the area within which vehicles traveling upon different streets joining at any other angle may come in conflict.
\item[MAY] The act referred to is permissive.
\item[MISDEMEANOR] The crime for which a sentence of not more than 90 days or a fine of not more than \$1,000, or both, may be imposed.
\item[MONTH] A calendar month.
\item[OATH] An affirmation in all cases in which, by law, an affirmation may be substituted for an oath, and in those cases the words \textbf{SWEAR} and \textbf{SWORN} shall be equivalent to the words \textbf{AFFIRM} and \textbf{AFFIRMED}.  All terms shall mean a pledge taken by the person and administered by an individual authorized by state law.
\item[OFFICER, OFFICE, EMPLOYEE, COMMISSION, or DEPARTMENT] An officer, office, employee, commission, or department of this city unless the context clearly requires otherwise.
\item[ORDINANCE] An ordinance duly adopted by the City Council.
\item[PERSON] Extends to and includes an individual, person, persons, firm, corporation, co-partnership, trustee, lessee, or receiver.  Whenever used in any clause prescribing and imposing a penalty, the terms \textbf{PERSON} or \textbf{WHOEVER} as applied to any unincorporated entity shall mean the partners or members thereof, and as applied to corporations, the officers or agents thereof.
\item[PETTY MISDEMEANOR] An offense which does not constitute a crime, and for which a sentence of a fine of not more than \$300 may be imposed.
\item[POLICE OFFICER or PEACE OFFICER] Every officer, including special police, authorized to direct traffic, keep the peace, and appointed or employed for the purpose of law enforcement.
\item[PRECEDING or FOLLOWING] Next before or next after, respectively.
\item[PREMISES] Any lot, piece or parcel of land within a continuous boundary, whether publicly or privately owned, occupied or possessed.
\item[PRIVATE PROPERTY] All property not included within the definition of “public property” or “public place.”
\item[PUBLIC PROPERTY or PUBLIC PLACE] Any place, property or premises dedicated to public use, owned by or controlled by the city, including, but not limited to, streets, parks, or parking lots so owned or occupied.
\item[ROADWAY] That portion of a street improved, designed, or ordinarily used for vehicle travel.  In the event a street includes two or more separate roadways, the term \textbf{ROADWAY}, as used herein, shall refer to any roadway separately, but not all roadways collectively.
\item[SHALL] The act referred to is mandatory.
\item[SIGNATURE or SUBSCRIPTION] Includes a mark when the person cannot write.
\item[STATE] The State of Minnesota.
\item[STREET] The entire area dedicated to public use, or contained in an easement or other conveyance or grant to the city, and shall include, but not be limited to, roadways, boulevards, sidewalks, alleys, and other public property between lateral property lines in which a roadway lies.
\item[SUBCHAPTER] A division of a chapter, designated in this code by a heading in the chapter analysis and a capitalized heading in the body of the chapter, setting apart a group of sections related by the subject matter of the heading.  Not all chapters have subchapters.
\item[VIOLATE] This term includes failure to comply with.
\item[WRITTEN] Any representation of words, letters, or figures, whether by printing or otherwise.
\item[YEAR] A calendar year, unless otherwise expressed.
\end{description}



\section{Severability}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Severability}
If any provision of this code as now or later amended or its application to any person or circumstance is held invalid, the invalidity does not affect other provisions that can be given effect without the invalid provision or application.



\section{Reference to Other Sections}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Reference to Other Sections}
Whenever in one section reference is made to another section hereof, that reference shall extend and apply to the section referred to as subsequently amended, revised, recodified, or renumbered unless the subject matter is changed or materially altered by the amendment or revision.



\section{Reference to Offices}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Reference to Offices}
Reference to a public office or officer shall be deemed to apply to any office, officer, or employee of this city exercising the powers, duties, or functions contemplated in the provision, irrespective of any transfer of functions or change in the official title of the functionary.



\section{Errors and Omissions}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Errors and Omissions}
If a manifest error is discovered, consisting of the misspelling of any words; the omission of any word or words necessary to express the intention of the provisions affected; the use of a word or words to which no meaning can be attached; or the use of a word or words when another word or words was clearly intended to express the intent, the spelling shall be corrected and the word or words supplied, omitted, or substituted as will conform with the manifest intention, and the provisions shall have the same effect as though the correct words were contained in the text as originally published.  No alteration shall be made or permitted if any question exists regarding the nature or extent of the error.



\section{Official Time}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Official Time}
The official time, as established by applicable state and federal laws, shall be the official time within this city for the transaction of all city business.



\section{Reasonable Time}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Reasonable Time}
\subsection{}
In all cases where an ordinance requires an act to be done in a reasonable time or requires reasonable notice to be given, reasonable time or notice shall be deemed to mean the time which is necessary for a prompt performance of the act or the giving of the notice.
\subsection{}
The time within which an act is to be done, as herein provided, shall be computed by excluding the first day and including the last.  If the last day is a legal holiday or a Sunday, it shall be excluded.



\section{Ordinances Repealed}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Ordinances Repealed}
This code, from and after its effective date, shall contain all of the provisions of a general nature pertaining to the subjects herein enumerated and embraced.  All prior ordinances pertaining to the subjects treated by this code shall be deemed repealed from and after the effective date of this code.



\section{Ordinances Unaffected}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Ordinances Unaffected}
All ordinances of a temporary or special nature and all other ordinances pertaining to subjects not embraced in this code shall remain in full force and effect unless herein repealed expressly or by necessary implication.



\section{Effective Date of Ordinances}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Effective Date of Ordinances}
All ordinances passed by the legislative body requiring publication shall take effect from and after the due publication thereof, unless otherwise expressly provided.



\section{Repeal or Modification of Ordinance}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Repeal or Modification of Ordinance}
\subsection{}
Whenever any ordinance or part of an ordinance shall be repealed or modified by a subsequent ordinance, the ordinance or part of an ordinance thus repealed or modified shall continue in force until the publication of the ordinance repealing or modifying it when publication is required to give effect to it, unless otherwise expressly provided.
\subsection{}
No suit, proceedings, right, fine, forfeiture, or penalty instituted, created, given, secured, or accrued under any ordinance previous to its repeal shall in any way be affected, released, or discharged, but may be prosecuted, enjoyed, and recovered as fully as if the ordinance had continued in force unless it is otherwise expressly provided.
\subsection{}
When any ordinance repealing a former ordinance, clause, or provision shall be itself repealed, the repeal shall not be construed to revive the former ordinance, clause, or provision, unless it is expressly provided.



\section{Ordinances Which Amend or Supplement Code}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Ordinances Which Amend or Supplement Code}
\subsection{}
If the City Council shall desire to amend any existing chapter, subchapter, section, subsection or item of this Code, the chapter, subchapter, section, subsection or item shall be specifically repealed and a new chapter, subchapter, section, subsection or item, containing the desired amendment, substituted in its place.
\subsection{}
Any ordinance which is proposed to add to the existing code a new chapter or section shall indicate, with reference to the arrangement of this code, the proper number of the chapter or section. In addition to this indication as may appear in the text of the proposed ordinance, a caption or title shall be shown in concise form above the ordinance.



\section{Preservation of Penalties, Offenses, Rights and Liabilities}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Preservation of Penalties, Offenses, Rights and Liabilities}
All offenses committed under laws in force prior to the effective date of this code shall be prosecuted and remain punishable as provided by those laws.  This code does not affect any rights or liabilities accrued, penalties incurred, or proceedings begun prior to the effective date of this code.  The liabilities, proceedings and rights are continued; punishments, penalties, or forfeitures shall be enforced and imposed as if this code had not been enacted.  In particular, any agreement granting permission to utilize highway right-of-ways, contracts entered into or franchises granted, the acceptance, establishment or vacation of any highway, and the election of corporate officers shall remain valid in all respects, as if this code had not been enacted.



\section{Copies of Code}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Copies of Code}
The official copy of this code shall be kept in the office of the City Clerk-Treasurer for public inspection.  The Clerk-Treasurer shall provide a copy for sale for a reasonable charge.



\section{Adoption of Statutes and Rules by Reference}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Adoption of Statutes and Rules by Reference}
It is the intention of the City Council that, when adopting this code, all future amendments to any state or federal rules and statutes adopted by reference in this code or referenced in this code are hereby adopted by reference or referenced as if they had been in existence at the time this code was adopted, unless there is clear intention expressed in the code to the contrary.



\section{Assignment of Duties}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!Assignment of Duties}
Whenever a specific duty is assigned to a particular officer or employee of the city, the designation or assignment shall also include the deputy, assistant or designee of the official or employee.


\setcounter{section}{98}
\section{General Penalty}
\index{CODE OF ORDINANCES; GENERAL PROVISIONS!General Penalty}
\subsection{}
Any person, firm, or corporation who violates any provision of this code for which another penalty is not specifically provided, shall, upon conviction, be guilty of a misdemeanor.  The penalty which may be imposed for any crime which is a misdemeanor under this code, including Minnesota Statutes specifically adopted by reference, shall be a sentence of not more than 90 days or a fine of not more than \$1,000, or both.
\subsection{}
Any person, firm or corporation who violates any provision of this code, including Minnesota Statutes specifically adopted by reference, which is designated to be a petty misdemeanor shall, upon conviction be guilty of a petty misdemeanor.  The penalty which may be imposed for any petty offense which is a petty misdemeanor shall be a sentence of a fine of not more than \$300.
\subsection{}
In either the case of a misdemeanor or a petty misdemeanor, the costs of prosecution may be added.  A separate offense shall be deemed committed upon each day during which a violation occurs or continues.
\subsection{}
The failure of any officer or employee of the city to perform any official duty imposed by this code shall not subject the officer or employee to the penalty imposed for a violation.
