\chapter*{Chapter 110: \\
	General Business Licensing}
    \addstarredchapter{Chapter 110: General Business Licensing}
    \minitoc
    \pagebreak

\section{Definitions\footnote{(‘83 Code, SEC. 6.01)}}
For the purpose of this title the following definitions shall apply, unless the context clearly indicates or requires a different meaning.
\begin{description}
    \item[APPLICANT]  Any person making an application for a license under this title.
    \item[APPLICATION]  A form with blanks or spaces thereon, to be filled in and completed by the applicant as a request for a license, furnished by the city and uniformly required as a prerequisite to the consideration of the issuance of a license for a business.
    \item[BOND]  A corporate surety document in the form and with the provisions acceptable and specifically approved by the City Attorney.
    \item[BUSINESS]  Any activity, occupation, sale of goods or services, or transaction that is either licensed or regulated, or both licensed and regulated, by the terms and conditions of this title.
    \item[LICENSE]  A document issued by the city to an applicant permitting the applicant to carry on and transact a business.
    \item[LICENSEE]  An applicant who, pursuant to an application, holds a valid, current, unexpired and unrevoked license from the city for carrying on a business.
    \item[LICENSE FEE]  The money paid to the city pursuant to an application and prior to issuance of a license to transact and carry on a business.
    \item[SALE, SELL and SOLD]  All forms of barter and all manner or means of furnishing merchandise to persons.
\end{description}

\section{Applications}
All applications shall be made as follows:
\subsection{}
All applications shall be made at the office of the Clerk-Treasurer upon forms that have been furnished by the city for such purposes.
\subsection{}
All applications must be subscribed, sworn to, and include the information as the Council shall deem necessary considering the nature of the business for which license application is made.
\subsection{}
It is unlawful for any applicant to intentionally make a false statement or omission upon any application form.  Any false statement in the application, or any willful omission to state any information called for on the application form, shall, upon discovery of the falsehood work an automatic refusal of license, or if already issued, shall render any license or permit issued pursuant thereto, void, and of no effect to protect the applicant from prosecution for violation of this chapter, or any part hereof.
\subsection{}
The Clerk-Treasurer shall, upon receipt of each application completed in accordance herewith, forthwith investigate the truth of statements made therein and the moral character and business reputation of each applicant for license to the extent as he or she deems necessary.  For the investigation the Clerk-Treasurer may enlist the aid of the Chief of Police.  The Council shall not consider an application before the investigation has been completed.
\subsection{}
Applications for renewal licenses may be made in the abbreviated form as the Council may by resolution adopt.\footnote{(‘83 Code, SEC. 6.02)  Penalty, see SEC. 110.99}

\section{Grant, Issuance, Transfer, Duplicate License and Renewal}
\subsection{Granting}
The Council may grant any application for the period of the remainder of the then current calendar year or for the entire ensuing license year.  All applications, including proposed license periods, must be consistent with this title.
\subsection{Issuing}
If an application is approved, the Clerk-Treasurer shall forthwith issue a license pursuant thereto in the form prescribed by the Council upon proof of ownership, payment of the appropriate license fee, and approval of the bond or insurance as to form and surety or carrier, if required.  All licenses shall be on a calendar year basis unless otherwise specified herein as to particular businesses.  Unless otherwise herein specified, license fees shall be pro-rated on the basis of one-twelfth for each calendar month or part thereof remaining in the then current license year.  Provided, that for licenses where the fee is less than \$100 a minimum license fee equal to ½ of the annual license fee shall be charged.  Except as to licenses which are specifically city-wide, licenses shall be valid only at one location and on the premises therein described.
\subsection{Transfer}
A license shall be transferable between persons upon consent of the Council.  No license shall be transferable to a different location without prior consent of the Council and upon payment of the fee for a duplicate license.  It is unlawful to make any transfer in violation of this division (C).
\subsection{Termination}
Licenses shall terminate only by expiration or revocation.
\subsection{Refusal and Revocation}
The Council may, for any reasonable cause, refuse to grant any application, or revoke any license.  No license shall be granted to a person of questionable moral character or business reputation.  Before revocation of any license, the Council shall give notice to the licensee and grant the licensee opportunity to be heard.  Notice to be given and the exact time of hearing shall be stated in the resolution calling for the hearing.
\subsection{Duplicate License}
Duplicates of all original licenses may be issued by the Clerk-Treasurer, without action by the Council, upon licensee’s affidavit that the original has been lost, and upon payment, to be determined by Clerk’s Office, for issuance of the duplicate.  All duplicate licenses shall be clearly marked \textbf{DUPLICATE}.\footnote{(‘83 Code, SEC. 6.03)}
\subsection{Renewals}
Applications for renewal of an existing license shall be made at least 30 days prior to the date of expiration of the license, and shall contain the information as is required by the city.  This time requirement may be waived by the Council for good and sufficient cause.\footnote{(‘83 Code, SEC. 6.09)}

\section{License Fees}
Except as otherwise herein provided, all fees for licenses under this title shall be fixed and determined by the Council, adopted by resolution, and uniformly enforced.  The license fees may, from time-to-time, be amended by the Council by resolution.  A copy of the resolution setting forth currently effective license fees shall be kept on file in the office of the Clerk-Treasurer, and open to inspection during regular business hours.  For the purpose of fixing the fees, the Council may subdivide and categorize licenses under a specific license requirement, provided, that any subdivision or categorization shall be included in the resolution authorized by this section.\footnote{(‘83 Code, SEC. 6.04)}

\section{Carrying or Posting of License}
All solicitors shall at all times when so engaged, carry their license on their person.  All other licensees shall post their licenses in their place of business near the licensed activity.  Provided, however, that in the case of machine or other device licensing, the city may provide a sticker for the current license year which shall be affixed to each machine or device requiring the sticker.  All licensees shall display their licenses upon demand by any officer or citizen.\footnote{(‘83 Code, SEC. 6.05)}

\section{Responsibility of Property Owner}
It is unlawful for any person to knowingly permit any real property owned or controlled by him to be used, without a license, for any business for which a license is required by this title.\footnote{(‘83 Code, SEC. 6.06)  Penalty, see SEC. 110.99}

\section{Responsibility of Licensee}
The conduct of agents or employees of a licensee, while engaged in performance of their duties for their principal or employer under the license, shall be deemed the conduct of the licensee.\footnote{(‘83 Code, SEC. 6.07)  Penalty, see SEC. 110.99}

\section{Conditional Licenses}
Notwithstanding any provision of law to the contrary, the Council may, upon a finding of the necessity therefor, place the conditions and restrictions upon a license as it, in its discretion, may deem reasonable and justified.\footnote{(‘83 Code, SEC. 6.08)}

\section{Insurance Requirements}
Whenever insurance is required by a section of this title, after approval by the Council, but before the license shall issue, the applicant shall file with the Clerk-Treasurer a policy or certificate of public liability insurance showing that the limits are at least as high as required, that coverage is effective for at least the license term approved, and that the insurance will not be cancelled or terminated without 30 days’ written notice served upon the Clerk-Treasurer.  Cancellation or termination of the coverage shall be grounds for license revocation.\footnote{(‘83 Code, SEC. 6.10)}

\section{Authority of Council as to Denial, Rates and Hearing}
\subsection{Right to Deny}
The Council reserves to itself the right to deny any application for a license to operate any business licensed or regulated under this title where the business involves service to the public, rates charged for service, use of public streets or other public property by the applicant or the public, or the public health, safety and convenience.  The Council may also consider the location of the business in making the determination.  Provided, however, that before making the determination, the Council shall hold a public hearing thereon pursuant to the notice to interested parties and the public as it may deem necessary or proper in action calling for the hearing.
\subsection{Rates}
Where, under specific provisions of this title, the Council has reserved to itself the right to fix or approve fees, rates or charges of a licensed or regulated business, the rates shall be uniform for each category or class of service, and no licensee or proprietor of a regulated business shall claim or demand payment in excess thereof.
\subsection{Hearing}
Any applicant or licensee under this title who challenges denial of a license or rates fixed or approved by the Council shall have a right to a hearing before the Council upon written request therefor.  Notice of time, place and purpose of the hearing shall be given to the persons and by the means as the Council may determine in calling the hearing.\footnote{(‘83 Code, SEC. 6.11)}

\setcounter{section}{98}
\section{Penalty}
Every person violates a section, subdivision, paragraph or provision of this title when he or she performs an act thereby prohibited or declared unlawful, or fails to act when the failure is thereby prohibited or declared unlawful, and upon conviction thereof, shall be punished as for a misdemeanor except as otherwise stated in specific provisions hereof.  The penalty which may be imposed for any crime which is a misdemeanor under this code, including Minnesota Statutes specifically adopted by reference, shall be a sentence of not more than 90 days or a fine of not more than \$1,000, or both.  The costs of prosecution may be added.  A separate offense shall be deemed committed upon each day during which a violation occurs or continues.\footnote{(‘83 Code, SEC. 6.99)}
