\chapter*{Chapter 118: \\
	Taxicabs}
    \addstarredchapter{Chapter 118: Taxicabs}
    \minitoc
    \pagebreak

\section{Definitions}

\begin{description}
    \item[FOR HIRE] For remuneration or compensation of any kind promised, paid or given to or received by a person for the transportation of persons or property within and upon the city streets and includes compensation obtained by an operator, driver or other persons indirectly by subtraction of the purchase price or addition to the selling price of property transported, when the purchase or sale of the property is not a bona fide purchase or sale.
    \item[OPERATOR] Any person, partnership, corporation or other legal entity to whom a license has been issued to engage in the business of operating a taxicab or a personal transportation vehicle.
    \item[TAXICAB AND PERSONAL TRANSPORTATION VEHICLES] A motor vehicle engaged in the for hire transportation of property or passengers, in form of fare or other remuneration, having a seating capacity of seven persons or less, including the driver, and not operated on a fixed route.
    \item[MOTOR CARRIERS] A person engaged in the for-hire transportation of property or passengers.
\end{description}

\section{License Required}
It is unlawful for any person or operator to drive or operate a taxicab or personal transportation vehicle within the City without a license issued by the City for the vehicle to be operated as a taxicab or personal transportation vehicle.  The owner, operator and driver are equally culpable and may be charged criminally under this chapter.

\section{Application for License}
An application for a taxicab or personal transportation vehicle license shall be filed with the Clerk on forms provided by the Clerk and such application shall be verified under oath and shall contain the information required in the following paragraphs.
\begin{enumerate}[{\indent}A)]
    \item The name and address of the applicant, and company name, if any, under which applicant intends to operate.
    \item The location from which such taxicabs or personal transportation vehicles shall be operated.
    \item A complete description of each vehicle to be operated including the license number, the vehicle identification, the color of the vehicle, make, model and year.
    \item Before issuing a taxicab license, the applicant shall present to the Council a certificate signed by a competent and experienced mechanic showing that the taxicab conveyance is in good mechanical condition, that it is fairly safe for transportation of passengers and that it is in neat and clean condition.  The similar certificate may be required from time to time during the license.  In lieu of the certificate, the Council makes up the report of the Chief of Police relative thereto.
    \item The employment history of the applicant.
    \item Whether or not the applicant has ever been convicted of a felony.
    \item Such other information as the city may from time to time require.
\end{enumerate}

\section{Police Investigation}
Prior to submitting an application for a taxicab or personal transportation vehicle license to the Council, the Clerk shall request an investigation and report from the Police Department as to the facts stated in the application and to the applicant’s traffic and police record.

\section{Council Procedure}
The Clerk and the Chief of Police shall meet and review the police record of the applicant.  The Clerk shall submit to the Council at a regular meeting thereof the application and any information deemed important by the Clerk or the Chief of Police, and any member of the public shall have an opportunity to be heard on the granting or refusal to grant a license.  If the Council finds and determines that the public interest is not served by the issuance of a license to the applicant, the applicant may not make reapplication for a license to operate a taxicab or personal transportation vehicle in the City until six months thereafter.

\section{License Fee}
If the Council approves the license on such application, a license shall be issued to the applicant upon the payment of the required license fee as established by Council Resolution.  A new license for each succeeding year may be issued upon the payment of a like fee unless the license has been revoked as provided herein.

\section{Revocation of License}
The license of any operator under this chapter may be revoked for failing or refusing to comply with the provisions of this chapter, or for the failure of any driver of a taxicab or personal transportation vehicle to comply with the provisions of this chapter, or for the failure of any driver of a taxicab or personal transportation vehicle to comply with any local, state, or federal law while driving a taxicab or personal transportation vehicle.  Such revocation will be pursuant to a hearing before the Council at which the license holder shall have an opportunity to present evidence on his or her behalf.

\section{Inspection of Vehicles and Equipment}
Every holder of a license under this chapter shall keep such vehicle in good serviceable condition so that each vehicle may be safely operated at all times without endangering the safety or property of the passengers carried or other persons.  The licensee shall annually have the vehicle inspected by a competent and experienced mechanic and shall produce a record of such inspection to authorized city personnel during regular business hours.  The license for the operation of any vehicle not kept in a safe and serviceable condition may, upon ten days mailed notice, in the discretion of the City Council, be revoked.

\section{Designation of Taxicabs or Personal Transportation Vehicles}
Each taxicab or personal transportation vehicle shall bear on the exterior surface of the body in letters not less than two inches in height the name of the owner or the company name under which the owner operates, and in addition may bear an identification design approved by the Council.  No owner whose identifying design, monogram or insignia to be used thereon shall conflict with or imitate any other color scheme, identifying design, monogram or insignia used on a vehicle or vehicles already operating under the chapter, in such a manner as to be misleading or tend to deceive or default the public, and further providing that if, after a license has been issued for a taxicab or personal transportation vehicle hereunder, identifying design, monogram or insignia thereof is changed so as to be in conflict with or imitate any identifying design, monogram or insignia used by any other person, owner or operator, in such manner as to be misleading or tend to deceive the public, the license covering such taxicab or personal transportation vehicle may be revoked.

\section{License Issuance and Display}
All licenses shall be issued for specific conveyances, except as otherwise herein provided.  License tags, including the number and year for which issued, shall be plainly visible on the dashboard of the conveyance.  Both sides of every licensed taxicab, when in use, shall be plainly and permanently marked as such with a painted sign or appurtenance showing the full or abbreviated name of the licensed operator.

\section{Rates}
Each applicant shall file with the Clerk, before a taxicab or personal transportation vehicle license is issued or renewed, a schedule of proposed maximum rates to be charged by the applicant during the licensed period for which the application is made.  Such schedule shall be posted in a conspicuous place in the taxicab or personal transportation vehicle in full view of passengers riding therein.

\section{Drivers of Taxicabs and Personal Transportation Vehicles}
Qualifications for drivers of taxicabs or personal transportation vehicles are as follows:
\subsection{}
Operators shall maintain the following standards for all drivers of taxicabs and personal transportation vehicles:
\subsubsection{}
Each driver must:
\begin{enumerate}[{\indent}a)]
    \item Possess a valid driver’s license to operate a motor vehicle in the State of Minnesota, which is valid for the class of vehicle driven;
    \item Be at least 18 years of age; and
    \item For the past three years:
        \begin{enumerate}[{\indent}i)]
            \item Have not had a driver’s license canceled under M.S. \textsection 171.14, as it may be amended from time to time, revoked under M.S. \textsection 171.17, as it may be amended from time to time, or suspended under M.S. \textsection 171.18, clause (2), (3), (4), (5), (7) or (11), as it may be amended from time to time;
            \item Have a driving record clear of convictions for operating a motor vehicle or motorcycle without insurance as required by M.S. \textsection 169.797, it may be amended from time to time; and
            \item Have a driving record clear of convictions for driving a motor vehicle without a valid current license for the class of vehicle driven; and
            \item Have a driving and criminal record clear of convictions for driving under the influence of alcohol or a controlled substance under M.S. \textsection 169A, as it may be amended from time to time, or a chapter in conformity with that section, of alcohol-related driving by commercial vehicle drivers under M.S. \textsection 169A.20, as it may be amended from time to time, and of driver’s license revocations under M.S. \textsection 169A.20, as it may be amended from time to time.
        \end{enumerate}
\end{enumerate}
\subsubsection{}
Each driver must also have a criminal record clear of convictions of crimes and anticipatory crimes against persons and crimes of anticipatory crimes reasonably related to providing transportation services.  For purposes of this part, “criminal record” means a conviction in which the date of discharge from the criminal sentence imposed is less than 15 years from the date of application.  The following Minnesota offenses or equivalent offenses from another state or jurisdiction are considered crimes against persons, or reasonably related to providing transportation services, or both:
\begin{enumerate}[{\indent}1)]
    \item Felony level conviction of M.S. \textsection 609.17, attempts;
    \item Felony level conviction of M.S. \textsection 609.175, conspiracy;
    \item M.S. \textsection 609.185, murder in the first degree;
    \item M.S. \textsection 609.19, murder in the second degree;
    \item M.S. \textsection 609.195, murder in the third degree;
    \item M.S. \textsection 609.20, manslaughter in the first degree;
    \item M.S. \textsection 609.205, manslaughter in the second degree;
    \item M.S. \textsection 609.21, criminal vehicular homicide and injury;
    \item M.S. \textsection 609.215, suicide;
    \item M.S. \textsection 609.221, assault in the first degree;
    \item M.S. \textsection 609.222, assault in the second degree;
    \item M.S. \textsection 609.223, assault in the third degree;
    \item M.S. \textsection 609.2231, assault in the fourth degree;
    \item Felony level violation of M.S. \textsection 609.224, assault in the fifth degree;
    \item M.S. \textsection 609.2247, domestic assault by strangulation;
    \item M.S. \textsection 609.228, great bodily harm caused by distribution of drugs;
    \item M.S. \textsection 609.23, mistreatment of persons confined;
    \item M.S. \textsection 609.2325, criminal abuse;
    \item M.S. \textsection 609.235, use of drugs to injure or facilitate crime;
    \item M.S. \textsection 609.24, simple robbery;
    \item M.S. \textsection 609.245, aggravated robbery;
    \item M.S. \textsection 609.25, kidnapping;
    \item M.S. \textsection 609.255, false imprisonment;
    \item M.S. \textsection 609.265, abduction;
    \item M.S. \textsection 609.2661, murder of an unborn child in the first degree;
    \item M.S. \textsection 609.2662, murder of an unborn child in the second degree;
    \item M.S. \textsection 609.2663, murder of an unborn child in the third degree;
    \item M.S. \textsection 609.2664, manslaughter of an unborn child in the first degree;
    \item M.S. \textsection 609.2265, manslaughter of an unborn child in the second degree;
    \item M.S. \textsection 609.267, assault of an unborn child in the first degree;
    \item M.S. \textsection 609.2671, assault of an unborn child in the second degree;
    \item M.S. \textsection 609.2672, assault of an unborn child in the third degree;
    \item M.S. \textsection 609.268, injury or death of an unborn child in the commission of a crime;
    \item M.S. \textsection 609.322, solicitation, inducement, and promotion of prostitution;
    \item M.S. \textsection 609.324, patrons, prostitutes, housing individuals engaged in prostitution;
    \item M.S. \textsection 609.33, disorderly house;
    \item M.S. \textsection 609.342, criminal sexual conduct in the first degree;
    \item M.S. \textsection 609.343, criminal sexual conduct in the second degree;
    \item M.S. \textsection 609.344, criminal sexual conduct in the third degree;
    \item M.S. \textsection 609.345, criminal sexual conduct in the fourth degree;
    \item M.S. \textsection 609.3451, criminal sexual conduct in the fifth degree;
    \item M.S. \textsection 609.352, solicitation of children to engage in sexual conduct;
    \item M.S. \textsection 609.365, incest;
    \item M.S. \textsection 609.377, malicious punishment of a child;
    \item M.S. \textsection 609.378, neglect or endangerment of a child;
    \item M.S. \textsection 609.498, tampering with a witness;
    \item M.S. \textsection 609.561, arson in the first degree;
    \item M.S. \textsection 609.582, Subd. 1, burglary;
    \item Gross Misdemeanor or Felony level conviction of M.S. \textsection 617.23, indecent exposure;
    \item M.S. \textsection 617.241, obscene materials and performances;
    \item M.S. \textsection 617.243, indecent literature, distribution;
    \item M.S. \textsection 617.246, use of minors in sexual performance;
    \item M.S. \textsection 617.247, possession of pornographic work involving minors;
    \item M.S. \textsection 617.293, harmful materials; dissemination and display to minors; and
    \item Felony convictions under M.S. Ch. 152, prohibited drugs.
\end{enumerate}
\subsection{Operator’s Responsibility}
Before using or hiring a driver the operator shall provide sufficient information regarding the driver’s identity to allow the Crookston Police Department to determine whether the driver has a valid driver’s license to operate a motor vehicle in the State of Minnesota for the class of vehicle driven and must conduct a review of the driving and criminal record of the driver.  The operator shall provide this information annually to the Crookston Police Department for each person continuing employment as a driver.  The driving and criminal record review must include an examination of the records of the Department of Public Safety, Division of Driver and Vehicle Services to determine if the driver meets the standards of Section 118.12 (A)(1).  The review must also include an examination of the conviction records of the Minnesota Bureau of Criminal Apprehension to determine if the driver has a criminal record of convictions for crimes listed in Section 118.12 (A)(1).
\subsection{Complaint Records}
Operator shall keep a record of complaint, report or allegation of misconduct made against a driver it uses or employs. The record must contain a copy of the complaint or report or a detailed written summary of the allegation.  Operator shall investigate the accuracy of the complaint, report, or allegation and shall include a summary of the investigation and resulting action taken, if any, in the record. These records must be included in the driver’s file or in a separate file kept by the operator.
\subsection{Liability Insurance Required}
No license to operate a taxicab or personal transportation vehicle shall be issued by the city until a certificate of insurance has been filed with the Clerk establishing that there is in full force and effect a liability policy issued by an insurance company authorized to do business in the State of Minnesota for each vehicle authorized to be operated by the applicant in the amount of \$500,000 for bodily injury to or death of any one person in a single accident, subject to a maximum of \$500,000 for injuries to two or more persons which are sustained in any one accident and \$100,000 for the destruction of or damage to property in a single accident.  In addition, the applicant shall provide uninsured and underinsured motorist coverage and basic economic loss benefits as outlined under M.S. \textsection 65B, as it may be amended from time to time.  An applicant shall obtain a certificate of insurance for each vehicle that is operated.  The applicant’s insurer shall mail the certificate of insurance to the Clerk, City of Crookston, 124 North Broadway, Crookston, MN 56716.  The certificate must show the vehicles covered by the policy and the policy limits.  Each policy shall provide that the city shall receive at least ten days written notice prior to cancellation of such policy.
